\documentclass[twocolumn]{ctexbook}
\usepackage{xcolor}

\newcommand{\phrase}[1]{{\colorbox{yellow!40}{#1}}}
\newcommand{\point}[1]{{\color{red}#1}}
\newcommand{\word}[1]{{\em\color{black}{#1}}}
\newcommand{\sentence}[1]{{\colorbox[gray]{0.8}{#1}}}
\newcommand{\expand}[1]{{\Large\colorbox{-red!90}{#1}}}

\begin{document}
	
	\part{unit 1}
	\section{conversation n.[c]}
	含义：\\
	沟通感情，交流想法的谈话。\\
	a \phrase{long/short} conversation\\
	an interesting/friendly conversation\\
	This is a \phrase{private \word{conversation}}\\
	\sentence{a conversation with my parents}\\
	\phrase{have a conversation}\\
	\sentence{have a long conversation with \ldots}\\
	\expand{dialogue}\\
	用法：\\
	make up a dialogue\\
	\section{until prep.}
	含义:\\
	某件事一直持续到某点结束；\\
	do sth. until a moment\\
	注意：\\
	1.do 是长动作\\
	2.prep.+n.介词短语\\
	例句:\begin{quote}
		Good til the last drop.\\
		Good till the last drop.\\
		Good until the last drop.\\
	\end{quote}
	\phrase{stay in bed 睡懒觉}\\
	\section{spoil vt.}
	错误翻译：毁掉\\
	含义：\\
	让{\color{red}原本美好}的事物变得{\color{red}糟糕}\\
	举例：\\
	Postcards always spoil my holiday.\\
	spoil (spoiled/spoiled)  \\
	The fly spoiled the nice meal.  \\
	The pinples spoil my face.\\
	The big pimple is spoiling my face.\\
	\section{receive vt.}
	含义：\\
	收到电话，短信，邮件等{\point{电子信息}}。\\
	搭配：\\
	{\point{receive}} a letter/mail/message\\
	类比：\\
	{\point{receive}} a message {\point{from}} sb.\\
	{\point{send}} a message {\point{to}} sb.\\
	举例：\\
	receive a message from my mon.\\
	send a message to her son.\\
	\section{request n.[c]}
	{\phrase{a request for sth.}}\\
	a request for money\\
	{\phrase{make a request}}\\
	I have already made a request for help.\\
	{\phrase{a \point{polite/strange/urgent} \word{request}}}\\
	\section{food n.[u]}
	含义：\\
	人或动物所吃的东西；\\
	注意：\\
	食物整体，不可数名词；\\
	eg:\\
	He ate the {\word{food}} and drink the beer.\\
	{\phrase{a litte/little/a lot of}\word{food}}\\
	{\phrase{eat/have }\word{food}}\\
	{\phrase{delicious/healthy/fast/junk}\word{food}}\\
	具体：\\
	{\word{breakfast/lunch/supper/dinner}}\\
	\begin{quote}
		Eat breakfast like a king,\\
		lunch like a prince,\\
		supper like a pauper.\\
	\end{quote}
	I have healthy food for breakfast.\\
	I eat a lot of food for lunch.\\
	I eat little food for supper.\\
	\section{diamond n.[n、c]}
	含义：\\
	人类所发现自然界最坚硬的矿物；\\
	A {\word{diamond}} is forever.\\
	钻石恒久远，一颗永流转。\\
	a {\word{diamond}}ring/necklace/earring\\
	搭配：\\
	buy/wear/sell a \word{diamond} ring/necklace\\
	注意：耳环是一对！\\
	wear a pair of diamond earrings\\
	\section{competition n.[c]}
	含义：\\
	众人参与相互竞争的活动；\\
	Nearly everybody enters for 'The Nicest Garden Competitioin'.\\
	\phrase{enter for a competition}\\
	\phrase{take part in a competition}\\
	\phrase{win/lose a competition}\\
	\phrase{hold/host a competition}\\
	结构：a名词 + competition \\
	\phrase{a dancing/painting/bodybuilding \word{competition}}\\
	This competition was held on the Thames last month.\\
	\section{crowd n.[c]}
	含义：\\
	为了\point{同一目的}而\point{聚集}的人群\\
	A large crowd of people had gathered under the clock.\\
	\phrase{a big/large/small crowd}\\
	\phrase{a crowd of \ldots (people/shoppers)}\\
	crowd\point{s} of tourists and passengers\\
	注意：\\
	crowd 是集合名词，谓语常用\point{单数}\\
	\phrase{a crowed gathers}\\
	The large crowd is gathering on the beach.\\
	\section{damage vt.}
	含义：\\
	对人或者事物造成损伤；\\
	注意：物理损伤\\
	\begin{quote}
		Recently a visitor \word{damaged} it.\\
		Recently it \word{was damaged} by a visitor.\\
		提示：常用\point{被动}\\
		\begin{quote}
			A \point{damage} B\\
			B \point{be damaged} (by A)\\
			\sentence{The car was badly damaged}\\
		\end{quote}
	\end{quote}
	\section{salary n.[c]}
	含义：\\
	每个月获得的工作收入\\
	原文：He gets a good salary.\\
	直译：他有一份高工资。\\
	意译：他的工资很高。\\
	举例：\begin{quote}
		我的工资很高。\\
		My salary is good.\\
		I have a good salary.\\
	\end{quote}
	\phrase{get/recive/earn a salary}\\
	\phrase{a high/good/low \word{salary}}\\
	\sentence{My salary is 6000 yuan a month.}
	\sentence{I receive/get/earn a salary of six thousand yaun a month.}\point{中国人习惯}
	\section{proud adj.}
	含义：\\
	对\point{拥有}或\point{做过的事}感到愉悦；\\
	或因\point{某人}感到自豪。\\
	\sentence{We are very proud of him,}
	为你而骄傲\begin{quote}
		be prouod of you \\
		very/really proud of sb\\
		Today I am proud of the school.\\
		Tomorrow the school will be proud of me.\\
		feel proud of sb./sth.\\
		make sb. proud\\
	\end{quote}
	\section{experience n.[C]}
	含义：\\
	生活中发生的对人\point{有影响}的\point{事件}\\
	翻译：\point{经历}或\point{事情}\\
	\phrase{a good/great experience}\\
	\phrase{a bad/painful experience}\\
	\phrase{a pleasant/unpleasant experience}\\
	\point{have a adj. experience}\\
	\sentence{Starbucks is a great experience,and not just a great retail store.}\\
        \section{afford}
        含义\\
        有足够的钱购买或支付某物；\\
        \phrase{\point{can not} \word{afford} sth.}
        我买不起这不车子\\
        I can not afford this car .\\
        \phrase{can not afford to do }
        I can not afford a car \point{or} an apartment.\\
        I can not afford to have a girlfriengd.\\
        \section{traffic}
        含义：\\
        车辆形成的\point{流动的状态}
        搭配：adj.\\
        bad/terrible traffic\\
        heaby/busy traffic\\
        light traffic\\
        The \word{traffic} was \point{light} this morning busy.\\
        \sentence{There is a little/little/much traffic.}\\
        \section{appear vt.}
        含义：\\
        参与\point{电影，电视}或其他\point{演出}\\
        appear in a film/play\\
        appear in a few films(出演了几部电影）\\
        appear in a famous play(参与了一部著名喜剧的演出）\\
        \sentence{appear on television (as \ldots{}})
        \section{bill n.[c]}
        含义：\\
        详细罗列服务所收\point{费用}的单子；\\
        \word{账单}\\
        \phrase{the phone/heating bill \\ get/recive a bill\\pay the bill}\\
        pay the big/large bill 支付这样昂贵的账单\\
        a credit-card \word{bill} 信用卡账单\\
        \section{hurry vi.}
        含义：\\
        匆忙去\point{某地}或\point{做某事}\\
        原因：时间紧迫\\
        \section{waste v.}
        含义：\\
        并不明智地使用\point{时间，金钱或精力}\\
        \word{waste n.[U]}\\
        be a waste of time/momey/energy\\
        This moive is a waste of time.\\
        waste money \point{on} art\\
        boring people 无聊的人\\
        can \point{not} afford to \word{waste}\\
        I can not afford to waste my energy on WeChat.  我可受不了把时
        间花在微信上。\\
        \section{mad adj.}
        含义：\\
        非常生气（美式）\\
        be very/fairly mad\\
        be mad at sb.\\
        be mad about sth.\\
        go mad 发疯\\
        drive sb. mad \\
        \section{dream v.}
        含义:\\
        幻想某个不太可能发生的事情；\\
        dream of doing sth.\\
        always/often/never dream\\
        \section{manager n.[c]}
        含义：\\
        manage vt.\\
        managerment  n.[U]
        \section{pretend}
        含义：\\
        作出\point{虚假表现}让人相信某事是真的；\\
        \section{soundly adv.}
        含义：\\
        睡眠质量极佳；\\
        sleep\phrase{well/deeply/peacefully/soundly}\\
        \sentence{soud mind,sound body}\\
        \section{trouble}
        含义：\\
        任何问题，麻烦，担忧，障碍等；\\
        数量：a lot of/little/ a little trouble\\
        性质：have trouble with sb./sth.\\
        have little trouble with neigbour\\
        I have never had any trouble with anyone\\

        \section{employ}
        含义：\\
        付钱给某人为你工作\\
        empoly sb. as sb.\\
        employ sb. \\
        be empolyed \\
        sb. be emplpyed as sb.\\
        employ sb, to do sth.\\
        sb.  be employed to do sth.\\
        \section{temptation n.}
        含义：\\
        强烈希望做某事或拥有某物\\
        \point{尽管并不合理；}\\
        the temptation to do  偷窃/花钱的诱惑\\
        搭配：great/huge/strong \word{temptation}\\
       have/ feel/resist the temptation to do \\
        Eve felt the temptation to eat the apple.\\
        I often feel the strong temptation to stay in bed.\\
        \section{explain v.}
        \point{清楚细致}的告诉某人某事；\\
        If you can't explain it simply,you don't understand it well enough.\\
        explain sth. (to sb.)\\
        explain why/how/what……\\
        Allow me to explain to you the rules of the game.\\
        \section{succeed vi.}
        达成心中所愿或既定目标。\\
        succeed well/beautifully\\
        We succeeded.\\
        succeed in doing sth.\\
        Our greatest weakness lies in giving up.The most certain way
        to succeed is asways to try just one more time.\\
        \section{design vt.}
        为即将制造的东西制作草图或细节。\\
        design sth.\\
        design a building/dress/logo\\
        design sth. for sth.\\
        \word{architect n.[C ]}\\
        design 被动式较多\\
        well/badly designed\\
        \section{inquire vt.}
        非常正式地询问消息；\\
        \sentence{inquire about sth./sb.}\\
        场合：十分正式；\\
        注意：inquire/enquire\\
        inquire why/how/when\ldots\\
        \section{difference n.}
        两个人或事物不同的部分；\\
        difference between A and B\\
        the  three  difference\point{s} between good and bad.\\
        know the difference\\
        can tell/see the difference \\
        \section{flight n.[c]}
        一次乘坐飞机的旅行；\\
        a flight from/to/across/……\\
        a long/short/comfortanle flight\\
        book/catch/miss a flight\\
        get on/off a flight\\
        \section{occer vi.}
        一个想法或主意突然降临\\
        an idea/thought occurs to sb.\\
        A good idea occured to me.\\
        sth. occur to sb,\\
        it occurs to sb, to do \\
        \sentence{My kids never think of visiting me.}\\
        地道: It never occers to my children to visit me.\\
      \end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: tx
%%% End:
